### 2019-09-04 manuscript/manuscript.tex
G's edits to supp

We also applied our temporal covariance approach to \texcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), negative covariances between dislike seasons (i.e. Spring 2010
and Fall 2011) when fluctuating selection is strong and acts genome-wide, as
the original study found. However, while we find temporal covariances that are
non-zero, we find only weak support for a seasonal fluctuating model driving
these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

>>>>

We also applied our temporal covariance approach to \texcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection \gc{in between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), negative covariances between dislike seasons (i.e. Spring 2010
and Fall 2011) when fluctuating selection is strong and acts genome-wide, as
the original study found. However, while we find temporal covariances that are
non-zero, we find only weak support for a seasonal fluctuating model driving
these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.
